\vspace{-2cm} Government websites as data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2018-12-16 paper/presentation/stmTopWordsINDem.tex
new structure

% latex table generated in R 3.4.2 by xtable 1.8-2 package
% Mon Nov 13 15:36:58 2017
\begin{table}[ht]
\centering
\begin{tabular}{llllll}
  \hline
-0.026 & -0.019 & -0.018 & -0.018 & -0.018 & -0.013 \\ 
  \hline
fort & propos & said & prosecutor & digest & fund \\ 
  citi & author & ask & charg & introduc & grant \\ 
  ordin & district & state & feloni & author & budget \\ 
  approv & street & will & counti & counti & counti \\ 
  purchas & public & chair & case & appoint & state \\ 
  depart & control & propos & crime & board & feder \\ 
  properti & amend & year & crimin & approv & depart \\ 
  will & intersect & move & offic & district & appropri \\ 
  resolut & counti & need & victim & fund & increas  \\ 
  contract & committe & council & sentenc & street & agenc \\ 
   \hline
\end{tabular}
%\caption{Top Democratic topics and words (Indiana), according to STM. 
%The words are the top words for the most Democratic/Republican topic, determined
%by the size (and significance) of the coefficient (see table header) of the party covariate.} 
\label{tabSTMINDem}
\end{table}

>>>>

% latex table generated in R 3.4.3 by xtable 1.8-2 package
% Tue Dec 26 20:59:22 2017
\begin{table}[ht]
\centering
\scriptsize
\begin{tabular}{llllll}
  \hline
-0.027 & -0.022 & -0.016 & -0.011 & -0.011 & -0.01 \\ 
  \hline
city & school & downtown & city & \cellcolor{blue!25}trash & \cellcolor{blue!25}housing \\ 
  ordinance & community & business & department & city & property \\ 
  approve & program & project & mayor & \cellcolor{blue!25}waste & program \\ 
  resolution & student & city & police & day & \cellcolor{blue!25}fund \\ 
  property & \cellcolor{blue!25}education & \cellcolor{blue!25}development & officer & \cellcolor{blue!25}recycle & home \\ 
  purchase & \cellcolor{blue!25}university & new & public & street & city \\ 
  area & national & center & citizen & collection & project \\ 
  department & award & \cellcolor{blue!25}economic & work & resident & neighborhood \\ 
  contract & high & company & safety & \cellcolor{blue!25}recycling & \cellcolor{blue!25}grant \\ 
  service & year & community & resident & snow & unit \\ 
   \hline
\end{tabular}
\caption{Top Democratic topics and words}%\caption{Top Democratic topics and words (Indiana), according to STM. 
%The words are the top words for the most Democratic/Republican topic, determined
%by the size (and significance) of the coefficient (see table header) of the party covariate.} 
\label{tabSTMINDem}
\end{table}

### 2018-12-16 paper/presentation/stmTopWordsINRep.tex
new structure

% latex table generated in R 3.4.2 by xtable 1.8-2 package
% Mon Nov 13 15:36:58 2017
\begin{table}[ht]
\centering
\begin{tabular}{llllll}
  \hline
0.024 & 0.019 & 0.019 & 0.016 & 0.016 & 0.016 \\ 
  \hline
motion & plan & inc & request & council & traffic \\ 
  second & zone & electr & board & citi & amp \\ 
  made & applic & build & member & ordin & vehicl \\ 
  approv & properti & construct & servic & common & stop \\ 
  mayor & approv & home & street & councilor & sign \\ 
  present & sign & street & approv & amend & road \\ 
  state & site & meridian & purchas & resolut & block \\ 
  will & locat & servic & citi & adopt & signal \\ 
  citi & commiss & west & move & wherea & street \\ 
  council & file & main & good & approv & driver \\ 
   \hline
\end{tabular}
%\caption{Top Republican topics and words (Indiana), according to STM. 
%The words are the top words for the most Democratic/Republican topic, determined
%by the size (and significance) of the coefficient (see table header) of the party covariate.} 
\label{tabSTMINRep}
\end{table}

>>>>

% latex table generated in R 3.4.3 by xtable 1.8-2 package
% Tue Dec 26 20:59:22 2017
\begin{table}[ht]
\centering
\scriptsize
\begin{tabular}{lllllll}
  \hline
 0.021 & 0.019 & 0.017 & 0.017 & 0.013 & 0.012 \\ 
  \hline
 foot & team & ave & request & amp & \cellcolor{red!25}building \\ 
   \cellcolor{red!25}sign & game & inc & board &\cellcolor{red!25} traffic & historic \\ 
   use & play & cross & member & stop & \cellcolor{red!25}build \\ 
   lot & league & creek & service & vehicle & material \\ 
   \cellcolor{red!25}building & camp & \cellcolor{red!25}construction & \cellcolor{red!25}street & block & preservation \\ 
   \cellcolor{red!25}zone & class & blvd & approve & sign & \cellcolor{red!25}wall \\ 
   area & age & park & city &  \cellcolor{red!25}airport & \cellcolor{red!25}roof \\ 
   district & must & lake & purchase & ave & window \\ 
   \cellcolor{red!25}parking & child & hill & move & theft & \cellcolor{red!25}floor \\ 
   residential & participant & ridge & good & signal & new \\ 
   \hline
\end{tabular}
\caption{Top Republican topics and words}%, according to STM. 
%The words are the top words for the most Democratic/Republican topic, determined
%by the size (and significance) of the coefficient (see table header) of the party covariate.} 
\label{tabSTMINRep}
\end{table}

### 2018-12-16 paper/tables/stmTopWordsINDem.tex
new structure

% latex table generated in R 3.4.2 by xtable 1.8-2 package
% Mon Nov 13 15:36:58 2017
\begin{table}[ht]
\centering
\begin{tabular}{llllllll}
  \hline
-0.026 & -0.019 & -0.018 & -0.018 & -0.018 & -0.013 & -0.011 & -0.011 \\ 
  \hline
fort & propos & said & prosecutor & digest & fund & servic & plan \\ 
  citi & author & ask & charg & introduc & grant & inform & develop \\ 
  ordin & district & state & feloni & author & budget & board & communiti \\ 
  approv & street & will & counti & counti & counti & applic & citi \\ 
  purchas & public & chair & case & appoint & state & project & neighborhood \\ 
  depart & control & propos & crime & board & feder & approv & program \\ 
  properti & amend & year & crimin & approv & depart & technolog & provid \\ 
  will & intersect & move & offic & district & appropri & system & public \\ 
  resolut & counti & need & victim & fund & increas & manag & resourc \\ 
  contract & committe & council & sentenc & street & agenc & agreement & area \\ 
   \hline
\end{tabular}
\caption{Top Democratic topics and words (Indiana), according to STM. 
The words are the top words for the most Democratic/Republican topic, determined
by the size (and significance) of the coefficient (see table header) of the party covariate.} 
\label{tabSTMINDem}
\end{table}

>>>>

% latex table generated in R 3.4.3 by xtable 1.8-2 package
% Tue Dec 26 20:59:22 2017
\begin{table}[ht]
\centering
\begin{tabular}{llllllll}
  \hline
-0.027 & -0.022 & -0.016 & -0.015 & -0.012 & -0.011 & -0.011 & -0.01 \\ 
  \hline
city & school & downtown & service & contract & city & trash & housing \\ 
  ordinance & community & business & division & bid & department & city & property \\ 
  approve & program & project & provide & contractor & mayor & waste & program \\ 
  resolution & student & city & city & city & police & day & fund \\ 
  property & education & development & management & agreement & officer & recycle & home \\ 
  purchase & university & new & public & work & public & street & city \\ 
  area & national & center & department & service & citizen & collection & project \\ 
  department & award & economic & program & department & work & resident & neighborhood \\ 
  contract & high & company & include & bidder & safety & recycling & grant \\ 
  service & year & community & office & move & resident & snow & unit \\ 
   \hline
\end{tabular}
\caption{Top Democratic topics and words (Indiana), according to STM. 
The words are the top words for the most Democratic/Republican topic, determined
by the size (and significance) of the coefficient (see table header) of the party covariate.} 
\label{tabSTMINDem}
\end{table}
